### 2018-08-04 sections/systematic_uncertainties.tex
some text fixes

In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a more prominent role, a more 
detailed treatment of its associated systematic uncertainties is made. In particular, since several analysis 
regions have a sufficiently large number of events of $\ttbin$ background, its normalisation is 
determined by the data during the fit procedure.
%, with no prior uncertainty assumed. 
In the case of the $\ttcin$ normalisation, a normalisation uncertainty of 50\% is assumed, as the fit to the data is unable 
to precisely determine it, and the analysis has very limited sensitivity to this uncertainty.
Since the diagrams that contribute to $\ttbar$+light-jets, $\ttcin$, $\ttbin$
production are different, all above uncertainties on $\ttbar$+jets
background modelling (NLO generator, PS \& Had, and radHi/radLow), except the uncertainty on the inclusive cross-section, are
considered to be uncorrelated among these processes.
Additional uncertainties on the $\ttbin$ background are considered associated with the NLO prediction from {\ShOL}, 
which is used for reweighting the nominal {\powheg}+{\pythiaeight} prediction. 
These include three different scale variations,  a different shower-recoil model scheme, and 
two alternative PDF sets (MSTW and NNPDF). Additional uncertainties are assessed for
the contributions to the $\ttbin$ background originating from multiple parton interactions.
Finally, an extra uncertainty on the $\ttbin$ background is assigned by comparing 
the predictions from {\powheg}+{\pythiaeight} and {\ShOL} 4F (5F vs 4F).
In the derivation of the above uncertainties, the overall normalisations of the \ttcin\ and \ttbin\ backgrounds 
at the particle level are fixed to the nominal prediction. In order to maintain the inclusive $\ttbar$ cross section, 
the normalisation of the $\ttbar$+light-jets background at the particle level is adjusted accordingly.
Further details are available in Ref.~\cite{Aaboud:2017rss}.

Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
of $W$+jets and $Z$+jets, and separately for $V$+light-jets, $V$+$\geq$1$c$+jets, and $V$+$\geq$1$b$+jets subprocesses.
The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
the different analysis regions considered, but requiring exactly 0 $b$-tagged jets. Agreement between data and predicted background 
in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour by about a factor
of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
subprocesses, considered uncorrelated between them.

@@

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted samples. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR". 
%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
%is applied as an uncertainty on the prediction in the nominal SR.
%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
%is applied as an uncertainty on the prediction in the nominal SR. 
%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
the shape difference between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
is applied as an uncertainty on the prediction in the nominal SR.
In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. Finally, the normalisation of the fake $\tauhad$ background in each SR is determined by the data during the fit procedure, and thus so is its uncertainty. In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.

@@

Several normalisation and shape uncertainties are taken into account for the $\Hq$ signal.
The uncertainty on the $\ttbar$ cross section also applies to the $\Hq$ signal and is taken to be the same as, 
and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background (see Sect.~\ref{sec:syst_bkgmodeling}).
Uncertainties on the Higgs boson branching ratios are taken into account
following the recommendation in Ref.~\cite{deFlorian:2016spz}.
%: $\pm 1.1\%$ ($\Delta\alpha_\textrm{S}$),  $\pm 1.4\%$ ($\Delta m_b$) and $\pm 0.8\%$ (theory).
Additional uncertainties associated with the modelling of additional radiation, with the choice of NLO generator, and
with the choice of parton shower and hadronisation model, are estimated from the comparison of the nominal
and alternative $\ttbar \to WbWb$ background samples (see discussion in Sect.~\ref{sec:syst_bkgmodeling}) and applied to $\Hq$ signal. 
These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.

>>>>

In the case of the $\Hbb$ search, where the $\ttbar$+HF background plays a more prominent role, a more 
detailed treatment of its associated systematic uncertainties is made. In particular, since several analysis 
regions have a sufficiently large number of events of \ttbin\ background, its normalisation is 
determined by the data during the fit procedure.
%, with no prior uncertainty assumed. 
In the case of the \ttcin\ normalisation, a normalisation uncertainty of 50\% is assumed, as the fit to the data is unable 
to precisely determine it, and the analysis has very limited sensitivity to this uncertainty.
Since the diagrams that contribute to $\ttbar$+light-jets, \ttcin, \ttbin\
production are different, all above uncertainties on $\ttbar$+jets
background modelling (NLO generator, PS \& Had, and radHi/radLow), except the uncertainty on the inclusive cross-section, are
considered to be uncorrelated among these processes.
Additional uncertainties on the \ttbin\ background are considered associated with the NLO prediction from {\ShOL}, 
which is used for reweighting the nominal {\powheg}+{\pythiaeight} prediction. 
These include three different scale variations,  a different shower-recoil model scheme, and 
two alternative PDF sets (MSTW and NNPDF). Additional uncertainties are assessed for
the contributions to the \ttbin\ background originating from multiple parton interactions.
Finally, an extra uncertainty on the \ttbin\ background is assigned by comparing 
the predictions from {\powheg}+{\pythiaeight} and {\ShOL} 4F (5F vs 4F).
In the derivation of the above uncertainties, the overall normalisations of the \ttcin\ and \ttbin\ backgrounds 
at the particle level are fixed to the nominal prediction. In order to maintain the inclusive $\ttbar$ cross section, 
the normalisation of the $\ttbar$+light-jets background at the particle level is adjusted accordingly.
Further details are available in Ref.~\cite{Aaboud:2017rss}.

Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
of $W$+jets and $Z$+jets, and separately for $V$+light-jets, $V$+$\geq$1$c$+jets, and $V$+$\geq$1$b$+jets subprocesses.
The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
the different analysis regions considered, but requiring exactly zero $b$-tagged jets. Agreement between data and predicted background 
in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour by about a factor
of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
subprocesses, considered uncorrelated between them.

@@

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted samples. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR". 
%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
%is applied as an uncertainty on the prediction in the nominal SR.
%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
%is applied as an uncertainty on the prediction in the nominal SR. 
%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
the shape difference between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
is applied as an uncertainty on the prediction in the nominal SR.
In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. 
In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\tauhad$ candidates 
between each SR and its corresponding CR in the $\ttbar$ simulation. 
Finally, the normalisation of the fake $\tauhad$ background in each SR is determined by the data during the fit procedure, and thus so is its uncertainty. 
%In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.

@@

Several normalisation and shape uncertainties are taken into account for the $\Hq$ signal.
The uncertainty on the $\ttbar$ cross section also applies to the $\Hq$ signal and is taken to be the same as, 
and fully correlated with, the uncertainty assigned to the $\ttbar \to WbWb$ background (see Sect.~\ref{sec:syst_bkgmodeling}).
Uncertainties on the Higgs boson branching ratios are taken into account
following the recommendation in Ref.~\cite{deFlorian:2016spz}.
%: $\pm 1.1\%$ ($\Delta\alpha_\textrm{S}$),  $\pm 1.4\%$ ($\Delta m_b$) and $\pm 0.8\%$ (theory).
Additional uncertainties associated with the modelling of additional radiation, with the choice of NLO generator, and
with the choice of parton shower and hadronisation model, are estimated from the comparison of the nominal
and alternative $\ttbar \to WbWb$ background samples (see discussion in Sect.~\ref{sec:syst_bkgmodeling}) and applied to $\Hq$ signal. 
These modelling uncertainties are taken to be uncorrelated with those affecting the $\ttbar \to WbWb$ background.
Finally, a 30\% uncertainty is assigned to the signal events with fake $\tauhad$ candidates selected by the $\Htautau$ search.
